Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-12 inc/conclusions.tex
more tweaks including adding a laser section to the conclusions

The Rose criterion~\cite{rose_television_1948} states that in order to have sufficient gray-scaling in a single-shot DTEM employing a 1k X 1k CCD camera for imaging, the pulse must contain at least $10^8$ electrons.
Additionally, the Child-Langmuir Law~\cite{child_discharge_1911,langmuir_effect_1923} governs the upper-limit of charge extraction in an electron gun. 
Pulses which short enough to be fully contained inside the acceleration region are subject to a modified form of Child-Langmuir Law~\cite{valfells_effects_2002}, which limits its the number of electrons $N_{crit}$ that may be generated by a laser of HW1/eM width $w$ before the pulse is subject to deleterious distortions,
\begin{equation}
  N_{crit} = \frac{\pi \varepsilon_0 w^2 V_{DC}}{e d} \,\text{,}
\end{equation}
where $V_{DC}$ and $d$ are the accelerator voltage and length respectively.
Due to this distinction, it is proposed that the term ``ultrafast'' should therefore be reserved for pulses of this type.
In order to satisfy the both the Rose criterion and this ultrafast Child-Langmuir restriction, we expect that UEM instruments will need to employ a relatively large-area emission source, typically of the order of $100\mu\text{m}$ HW1/eM width or greater.
This has necessitated building a custom acceleration region based on the design of Togawa \textit{et al.}~\cite{togawa_ceb6_2007} which boasts a moderately uniform acceleration field near the axis of the accelerator, as well as other large-aperture electron-optical elements for our prototype UEM column.
We have also designed and built a custom laser source capable of generating these electron pulses.

>>>>

The Rose criterion~\cite{rose_television_1948} states that in order to have sufficient gray-scaling in a single-shot DTEM employing a 1k X 1k CCD camera for imaging, the pulse must contain at least $10^8$ electrons.
Additionally, the Child-Langmuir Law~\cite{child_discharge_1911,langmuir_effect_1923} governs the upper-limit of charge extraction in an electron gun. 
Pulses which short enough to be fully contained inside the acceleration region are subject to a modified form of Child-Langmuir Law~\cite{valfells_effects_2002}, which limits its the number of electrons $N_{crit}$ that may be generated by a laser of HW1/eM width $w$ before the pulse is subject to deleterious distortions,
\begin{equation}
  N_{crit} = \frac{\pi \varepsilon_0 w^2 V_{DC}}{e d} \,\text{,}
\end{equation}
where $V_{DC}$ and $d$ are the accelerator voltage and length respectively.
Due to this distinction, it is proposed that the term ``ultrafast'' should therefore be reserved for pulses of this type.
In order to satisfy the both the Rose criterion and this ultrafast Child-Langmuir restriction, we expect that UEM instruments will need to employ a relatively large-area emission source, typically of the order of $100\mu\text{m}$ HW1/eM width or greater.
This has necessitated building a custom acceleration region based on the design of Togawa \textit{et al.}~\cite{togawa_ceb6_2007} which boasts a moderately uniform acceleration field near the axis of the accelerator, as well as other large-aperture electron-optical elements for our prototype UEM column.

We have also designed and built a custom laser source capable of generating these electron pulses.
The primary laser radiation source for the studies is a home-built, diode-pumped and thermal-lens-shaped, femtosecond Yb:KGW oscillator~\cite{berger_high-power_2008} delivering 250fs duration pulses at 1047nm and a 63MHz repetition rate.
This 2W average power laser is frequency doubled in a 3mm lithium triborate (LBO) crystal with 50\% efficiency to yield $\sim$200fs green pulses at 523nm (photon energy, $\hbar \omega$ = 2.37eV).
Further doubling with a cylindrical focusing geometry in a 7mm $\beta$-barium borate (BBO) crystal yields 261nm ($\hbar \omega$ = 4.75eV) UV pulses with a duration of $\sim$4ps (due to the 600fs/mm group velocity mismatch between the green and generated UV).
As an ancillary benefit of using an in-house built laser source, the cavity length may be changed; for soliton mode-locked lasers, this length is directly related to the repitition rate.
By tuning the length, we are able to frequency match a high harmonic of the repitition rate and the natural oscillation of the RF cavity.
This is done to synchronize the laser and the RF cavity in an essentially passive manner, obviating the need for expensive electronic devices which would be add deleterious electronic phase noise (jitter) to the system.

### 2013-04-12 inc/introduction.tex
more tweaks including adding a laser section to the conclusions

All of these considerations motivate the construction of the prototype UEM column being built by our group at UIC.
In Chapter \ref{chap:prototype}, I detail the design and fabrication of large-aperture electron-optical elements, which can readily admit these large width electron pulses; included among these are the accelerator and magnetic lenses.
Then, before I conclude, I will in Chapter \ref{chap:photocathode} highlight the photocathode engineering work which has been undertaken in an attempt to reduce the rms transverse momentum of the emitted electron pulses.
In fact, the search for a low transverse momentum electron source has applications beyond, UEM and UED; the fields of X-ray Free Electron Lasers (XFELs,~\cite{nemeth_high_2010}) and Compact X-ray Light Sources (CXLS) [ref] will also benefit from such a source.
I will present investigations of several different photoemission processes, some of which are yielding very promising results.
In fact, our recent work on excited-state thermionic emission~\cite{berger_excited_2012} may even challenge long-standing ideas about which materials and processes may hold the keys to low-emittance (or high-brightness) electron sources.

>>>>

All of these considerations motivate the construction of the prototype UEM column being built by our group at UIC.
In Chapter \ref{chap:prototype}, I detail the design and fabrication of large-aperture electron-optical elements, which can readily admit these large width electron pulses; included among these are the accelerator and magnetic lenses.
Then, before I conclude, I will in Chapter \ref{chap:photocathode} highlight the photocathode engineering work which has been undertaken in an attempt to reduce the rms transverse momentum of the emitted electron pulses.
In fact, the search for a low transverse momentum electron source has applications beyond UEM and UED; the fields of X-ray Free Electron Lasers (XFELs,~\cite{nemeth_high_2010}) and Compact X-ray Light Sources (CXLS) \cite{cxls_workshop_report_2012} will also benefit from such a source.
I will present investigations of several different photoemission processes, some of which are yielding very promising results.
In fact, our recent work on excited-state thermionic emission~\cite{berger_excited_2012} may even challenge long-standing ideas about which materials and processes may hold the keys to low-emittance (or high-brightness) electron sources.
